---
title: "Asset Classes"
output: 
  html_document:
    self_contained: true
    theme:
      bg: "#2B3E50"
      fg: "#EBEBEB"
      primary: "lime"
      secondary: "#51616F"
      base_font:
        google: Prompt
      heading_font:
        google: Prompt
      code_font:
        google: JetBrains Mono
---

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(dplyr)
library(lubridate)
library(gt)
library(ggplot2)
library(moments)
library(glue)


knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  fig.width = 9,
  fig.height = 6,
  fig.align = "center",
  tidy = FALSE,
  strip.white = TRUE,
  out.width = '100%'
)

bd_txt <-
  function(x,
           title = "Grading",
           subtitle = "-",
           width = 700) {
    if (nchar(gsub(" ", "", subtitle)) == 0) {
      subtitle <- "-"
    }
    y <- x %>% gt::gt() %>%
      gt::tab_header(title = title, subtitle = subtitle) %>%
      gt::tab_style(style = cell_text(weight = "bold"),
                    locations = cells_column_labels(colnames(.))) %>%
      gt::tab_style(style = list(
        cell_fill(color = "royalblue"),
        cell_text(color = "white", weight = "bold")
      ),
      locations = cells_title(groups = c("title")))
    y = y %>% tab_options(table.width = px(width),
                          table.font.size = pct(80))
    return(y)
  }

bd_lo <- function(x, width = 700) {
  y <- x %>% gt::gt(rowname_col = rownames(.)) %>%
    gt::tab_header(title = "Learning Objectives",
                   subtitle = "Desired Outcomes Sought for Mastery of Material") %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(
      cell_fill(color = "royalblue"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_title(groups = c("title")))
  y = y %>% tab_options(table.width = px(width),
                        table.font.size = pct(80))
  return(y)
}


from = as.Date("2014-01-01")
to = lubridate::rollback(Sys.Date())
tickers <-  c("TLT","USO","GLD","VNQ","SPY")
asset1 <- tickers[2] 
asset2 <- tickers[3] 
cors <- c(25,75,252)
```

##  {.tabset .tabset-pills}

+ This exercise consists in analyzing returns across multiple asset classes.
+ You are an analyst at a research firm tasked to prepare a report to be sent to clients. The firm expects from you a clean business document. 
+ For clarity, the expectations are that you took on the feedback from the first quiz and the standards are both higher now and more consequential if your performance is short of them. 
+ The clients, despite knowing markets at a high level, have a limited knowledge of Finance and statistics. So do NOT assume they know what you mean with acronyms or concepts. 
+ Add a summary at the beginning of your document with few short bullet points on what key messages they should draw from your analysis.   

### Skills Practiced & Requirements

+ Use of APIs for data extraction.
+ Data wrangling and parsing WITHOUT manual filtering or data.
+ Choice of effective visualization in communication with clean formatting.
+ Data analytics and an ability to tell a story from it.

### Data

+ US Long Term bonds with the [iShares 20+ Year Treasury Bond ETF](https://etfdb.com/etf/TLT/#etf-ticker-profile).
+ Energy Liquids with the [United States Oil Fund](https://etfdb.com/etf/USO/#etf-ticker-profile).
+ Gold with the [SPDR Gold Trust](https://etfdb.com/etf/GLD/#etf-ticker-profile).
+ Real Estate with the [Vanguard Real Estate Index Fund](https://etfdb.com/etf/VNQ/#etf-ticker-profile).
+ US equities with the [SPDR S&P 500 ETF](https://etfdb.com/etf/SPY/#etf-ticker-profile).

```{r}
tickers
```

### Your Ask

1. Extract data from `r from` to `r to` and compute daily `log()` returns adjusted for splits and dividends. Do not display in your document as this is the data wrangling of it and it serves no purpose in a business document.
2. Plot histograms of returns by asset class in a manner that you can effectively visualize the comparison.
3. Show a table of distribution moments of all assets. Complement with a short commentary on how they compare with a normal distribution.
4. Show a plot of the correlation matrix between all assets.
5. Show a chart of rolling correlations between `r asset1` and `r asset2` with windows of `r cors[1]`, `r cors[2]` and `r cors[3]` business days.
6. Compute the Jarque-Bera statistics on all assets

  + Display the results in a single table.
  + State which one(s) are normally distributed and why. 
7. Compute the Kolmogorov-Smirnov (“KS”) on `SPY` returns and state whether the results indicate that the returns are normally distributed.



