---
title: "Asset Classes"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(learnr)
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  fig.width = 9,
  fig.height = 6,
  fig.align = "center",
  tidy = FALSE,
  strip.white = TRUE,
  out.width = '100%'
)
library(gt)
bd_txt <-
  function(x,
           title = "Grading",
           subtitle = "-",
           width = 700) {
    if (nchar(gsub(" ", "", subtitle)) == 0) {
      subtitle <- "-"
    }
    y <- x %>% gt::gt() %>%
      gt::tab_header(title = title, subtitle = subtitle) %>%
      gt::tab_style(style = cell_text(weight = "bold"),
                    locations = cells_column_labels(colnames(.))) %>%
      gt::tab_style(style = list(
        cell_fill(color = "royalblue"),
        cell_text(color = "white", weight = "bold")
      ),
      locations = cells_title(groups = c("title")))
    y = y %>% tab_options(table.width = px(width),
                          table.font.size = pct(80))
    return(y)
  }

bd_lo <- function(x, width = 700) {
  y <- x %>% gt::gt(rowname_col = rownames(.)) %>%
    gt::tab_header(title = "Learning Objectives",
                   subtitle = "Desired Outcomes Sought for Mastery of Material") %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(
      cell_fill(color = "royalblue"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_title(groups = c("title")))
  y = y %>% tab_options(table.width = px(width),
                        table.font.size = pct(80))
  return(y)
}


from = as.Date("2008-01-01")
to = lubridate::rollback(Sys.Date())
```

## Problem We Are Solving

**This quiz consists in analysing financial returns across multiple asset classes.**

This exercise is quiz #2 - see grading section.

### Asset classes considered:

+ US Long Term bonds with the [iShares 20+ Year Treasury Bond ETF](https://etfdb.com/etf/TLT/#etf-ticker-profile).
+ Energy Liquids with the [United States Oil Fund](https://etfdb.com/etf/USO/#etf-ticker-profile).
+ Gold with the [SPDR Gold Trust](https://etfdb.com/etf/GLD/#etf-ticker-profile).
+ Real Estate with the [Vanguard Real Estate Index Fund](https://etfdb.com/etf/VNQ/#etf-ticker-profile).
+ US equities with the [SPDR S&P 500 ETF](https://etfdb.com/etf/SPY/#etf-ticker-profile).

```{r}
tickers <-  c("TLT","USO","GLD","VNQ","SPY")
```

### Your Ask

In a concise .Rmd using `tidy` (i.e. no `xts`), do the following:

1. Extract data from `r from` to `r to` and compute daily `log()` returns. It is not necessary to display in your document as this is the data wrangling of it.
2. Plot a histogram of returns by asset class.
3. Show a table of return distribution with each moments with a short commentary on they compare with a normal distribution.
4. Compute the Jarque-Bera statistics.

  + Display the results.
  + State which one are normally distributed and which ones are not. 
5. Compute the Kolmogorov-Smirnov (“KS”) on `SPY` returns and state whether the results indicate that the returns are normally distributed.

6. I am your business leader and, despite knowing markets at a high level, my Finance background is quite limited... Tell me in a few bullet points what the key messages I should draw from your analysis so I can cut and paste them in a Powerpoint to my boss. Add this section at the beginning of the document in a summary section.  


## Grading

At this point in the class, more differentiation will be applied in grading. This is an advanced class in your learning in your degree and/or professional workplace and you are judged both on absolute and relative standards versus your peers.

```{r, echo=F,include=TRUE, fig.height=3}
tibble(
  Competency = c("Summary",
                 "Presentation",
                 "Accuracy of code and results"),
  Measure = c(
    "Ability to distill and communicate the key findings.",
    "Professionally rendered presentations. Clean document of unnecessary clutter not relevant to the story. Assume I am a business leader and interested in the story, not how you got to it. Format properly your charts and tables.",
    "No errors in computations."
  ),
  Score = c("2 points",
            "2 points",
            "6 points")
) %>% bd_lo()
```

## Solution Hint

Sample formatted charts and tables.

```{r, echo = F, eval=T}
#from = "2008-01-01"
#to = "2021-01-31"

r = "adjusted"
#r = "close"

library(tidyquant)
ret <- tidyquant::tq_get(tickers,
              get  = "stock.prices",
              from = from,
              to = to) %>% 
  dplyr::transmute(date, symbol,value = get(r)) %>% 
  dplyr::group_by(symbol) %>% 
#  dplyr::mutate(ret = log(close / dplyr::lag(close))) %>% stats::na.omit() 
  dplyr::mutate(ret = log(value / dplyr::lag(value))) %>% stats::na.omit() 
```


```{r, r, echo = F, eval=T}
ret %>% ggplot(aes(x = ret, col = symbol, fill = symbol)) + 
  geom_histogram(aes(y = stat(width*density)), bins = 200,show.legend = FALSE) +
  geom_rug(col = "black") +
  facet_grid(symbol ~ .) +
  coord_cartesian(xlim = c(-max(abs(ret$ret)),max(abs(ret$ret))))+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Log Returns Density Histogram",
       y = "Density", x = "Log Returns")
```

```{r, echo = F, eval=T}
library(moments)
ret %>% 
  dplyr::summarise(mu = mean(ret),
                   sigma = sd(ret),
                   skew = moments::skewness(ret),
                   kurt = moments::kurtosis(ret),
                   .groups = "keep") %>% 
  dplyr::mutate(dplyr::across(where(is.numeric), round, 5)) %>% 
  dplyr::ungroup() %>% 
  bd_txt(title = "Distribution Moments", subtitle = "") %>% 
  gt::fmt_number(columns = c(skew,kurt), decimals = 2) %>% 
  gt::fmt_percent(columns = c(mu, sigma), decimals = 3)
```


```{r, echo = F, eval=T}
library(PerformanceAnalytics)
ret.wide <- ret %>%  
  tidyr::pivot_wider(date, names_from = symbol, values_from = ret) %>% 
  stats::na.omit() 
ret.wide %>% 
  timetk::tk_xts(rename_index = "date") %>% 
  PerformanceAnalytics::chart.Correlation()
```


```{r, echo = F, eval=T}
fig.title = "Correlation Instability"
library(tibbletime)
cor20 <- tibbletime::rollify(~cor(.x, .y),window = 20)
cor252 <- tibbletime::rollify(~cor(.x, .y),window = 252)
cor1000 <- tibbletime::rollify(~cor(.x, .y),window = 1000)
ret.wide %>% dplyr::mutate(cor20 = cor20(VNQ,SPY),
                           cor252 = cor252(VNQ,SPY),
                           cor1000 = cor1000(VNQ,SPY),
                           cor = cor(VNQ,SPY)) %>% 
  stats::na.omit() %>%
  dplyr::select(date,dplyr::starts_with("cor")) %>% 
  tidyr::pivot_longer(-date, "series","value") %>% 
  ggplot(aes(x = date,y = value, col = series)) + geom_line() +
  labs(title = fig.title,x = "",y = "")
```

```{r, echo = F, eval=T}
library(broom)
ret %>% dplyr::do(broom::tidy(tseries::jarque.bera.test(.$ret)))
```

```{r, echo = F, eval=T}
spy <- ret %>% dplyr::filter(symbol == "SPY") %>% ungroup() %>% dplyr::select(ret)
stats::ks.test(spy, y = "pnorm")
#stats::ks.test(rnorm(10000), y = "pnorm")
```


