---
title: "DSCF Quiz 1"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(learnr)
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = FALSE,
                      fig.width = 9, fig.height = 6,fig.align = "center",
                      tidy = FALSE, strip.white = TRUE, out.width = '100%')
library(gt)
bd_txt <- function(x,title = "Grading",subtitle = "-", width = 700) {
  if (nchar(gsub(" ","",subtitle))==0) {subtitle <- "-"}
  y <- x %>% gt::gt() %>%
    gt::tab_header(title = title, subtitle = subtitle) %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(cell_fill(color = "royalblue"),
                               cell_text(color = "white",weight = "bold")),
                  locations = cells_title(groups = c("title")))
  y= y %>% tab_options(table.width = px(width),table.font.size = pct(80))
  return(y)
}

bd_lo <- function(x,width=700) {
  y <- x %>% gt::gt(rowname_col = rownames(.)) %>%
    gt::tab_header(title = "Learning Objectives",
                   subtitle = "Desired Outcomes Sought for Mastery of Material") %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(cell_fill(color = "royalblue"),
                               cell_text(color = "white",weight = "bold")),
                  locations = cells_title(groups = c("title")))
  y= y %>% tab_options(table.width = px(width),table.font.size = pct(80))
  return(y)
}


from = as.Date(paste0(lubridate::year(Sys.Date()),"-01-01"))
to = lubridate::rollback(Sys.Date())

```

## Problem We Are Solving

**This quiz consists in analysing financial risk in ten stocks in the S&P500.**

The task consists in:

+ You are given 10 stock tickers in the S&P500.
+ Your leader knows you have recently acquired data science skills and is looking for a better way of doing things...
+ You need to measure the following for each `Symbol`:

  + Average daily return.
  + Standard Deviation.
  + Worst daily return performance.

+ Daily returns are `log()` returns.
+ Time period is from `r from` to `r to`.

## Timeline and Format

+ Send the results as a `.Rmd` and **properly rendering** `.html` via email before the next class.
+ Name your file `Quiz1_<lastname>_<firstname>`.

## Grading

```{r, echo=F,include=TRUE, fig.height=3}
tibble(Competency=c("RMardown",
                    "Presentation",
                    "Results"),
           Measure=c(".Rmd renders without errors.",
                   "It is readable as it would in a Word document and clear without unnecessary code and warnings being displayed.",
                   "Correct results"),
           Score=c("2 points",
                   "3 points",
                   "5 points")) %>% bd_lo()
```

## Stock Universe 

```{r, echo = F}
# library(rvest)
# url = "https://www.slickcharts.com/sp500"
# html <- xml2::read_html(url)
# x = html %>% html_table(.,fill=T) %>% .[[1]] %>% as_tibble() %>% 
#   dplyr::filter(dplyr::row_number() <= 5 | dplyr::row_number() %in% c(100,200,300,400,450)) %>% 
#   dplyr::select(Company, Symbol)
# x %>% bd_txt(title = "Companies and Symbols", subtitle = "use the relevant API from the Data Wrangling Module")

set.seed(1604)
r <- replicate(3,as.integer(runif(10,1,500)))
x <- RTLquiz::sp500_desc %>% 
  dplyr::select(Company = company, Symbol = symbol) %>% dplyr::slice(r[,ceiling(lubridate::month(Sys.Date()) / 4)])
x %>% bd_txt(title = "Companies and Symbols", subtitle = "use the relevant API from the Data Wrangling Module") #%>% gt::cols_width(starts_with("C") ~ px(150))
```

## Solution Hint

+ Refer to the training material you were provided,
+ Google it, or
+ Ask your peers for help.

```{r, echo = F, eval=T}
library(tidyquant)
tidyquant::tq_get(x$Symbol,
              get  = "stock.prices",
              from = from,
              to = to) %>% 
  dplyr::select(date, symbol,adjusted) %>% 
  dplyr::group_by(symbol) %>% 
  dplyr::mutate(ret = log(adjusted / dplyr::lag(adjusted))) %>% 
  stats::na.omit() %>% 
  dplyr::summarise(aveRet = mean(ret),
                   StdV = sd(ret),
                   WorstRet = min(ret)) %>% 
  dplyr::arrange(desc(aveRet)) %>%
  bd_txt(title = "Returns By Stock", subtitle = "Sorted by Ave Return") %>% 
  gt::fmt_percent(columns = vars(aveRet,StdV,WorstRet), decimals = 2)
```



