---
title: "Data Wrangling"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```


## Object Class 

**The data displayed is from the `mtcars` dataset from `tidyverse` until further notice.**

```{r class}
learnr::quiz(
  learnr::question("What function would you use to describe the x object class and structure in your environment?",
    learnr::answer("summary(x)"),
    learnr::answer("View(x)"),
    learnr::answer("str(x)", correct = TRUE),
    learnr::answer("?x"),
    allow_retry = T
  )
) 
```

## Piping

These questions deals with the `%>%` pipe operator?

```{r pipe}
learnr::quiz(
  learnr::question("The pipe operator:",
    learnr::answer("Allows one to smoke great tobacco."),
    learnr::answer("Assigns the result of an operation to a variable."),
    learnr::answer("Passes the output of left command into the input of the right command.", correct = TRUE),
    allow_retry = T
  )
)
```

You open a new `R` session, type `mtcars %>% dplyr::mutate(cyl = cyl +1)` and get this message:

`Error in mtcars %>% dplyr::mutate(cyl = cyl + 1) : could not find function "%>%"`


```{r pipelib}
learnr::quiz(
  learnr::question("What does it mean?",
    learnr::answer("I don't know."),
    learnr::answer("I forgot to load library(tidyverse).", correct = TRUE),
    learnr::answer("I forgot to load all my active libraries."),
    allow_retry = T
  )
)
```


The `%>%` operator can simplifies greatly coding logic. 

```{r pipelogic}
learnr::quiz(
  learnr::question("When faced with a sequence of piping operators, best practice to learn is to:",
    learnr::answer("Copy and paste the code provide by the Prof."),
    learnr::answer("Create my own copy of it in a .Rmd document and display it nicely."),
    learnr::answer("Be focused on executing each pipe one at a time with a view of understanding the input-transform-output sequence in terms of data class.", correct = TRUE),
    allow_retry = T
  )
)
```

## Subsetting 

```{r subset}
learnr::quiz(
  learnr::question("Which dplyr function would you use to subset a data frame?",
    learnr::answer("subset()"),
    learnr::answer("select()"),
    learnr::answer("filter()", correct = TRUE),
    allow_retry = T
  )
)
```

## Mutate and Transmute

```{r muttrans}
learnr::quiz(
  learnr::question("Select the TRUE statement(s) on what the functions do to a data frame.",
    learnr::answer("`mutate()` deletes a column and transmute() append a column."),
    learnr::answer("`transmute()` deletes a column and mutate() append a column."),
    learnr::answer("`transmute()` only returns the column created.", correct = TRUE),
    learnr::answer("`mutate()` returns the column created and existing columns.", correct = TRUE),
    allow_retry = T
  )
)
```

## Select

```{r,echo=FALSE}
x = mtcars %>% dplyr::mutate(car = rownames(mtcars)) %>% dplyr::select(mpg,cyl,car,dplyr::everything()) %>% as_tibble()
head(x)
```

```{r select}
learnr::quiz(
  learnr::question("Select the best command to re-order columns to show car first.",
    learnr::answer("x %>% dplyr::select(car,mpg,cyl,disp,hp,drat,wt,qsec,vs)"),
    learnr::answer("x %>% dplyr::select(car,everything)"),
    learnr::answer("x %>% dplyr::select(car,...)"),
    learnr::answer("x %>% dplyr::select(car,everything())", correct = TRUE),
    allow_retry = T
  )
)
```

## Filter

```{r, echo = F}
x %>% dplyr::filter(mpg >30 & cyl >= 4)
```

You are interested in filtering cars with a mpg > 30 and cyl >= 4.

```{r filter}
learnr::quiz(
  learnr::question("Which command(s) would give you the same information?",
    learnr::answer("x %>% dplyr::filter(mpg >30 & cyl >= 4)", correct = TRUE),
    learnr::answer("x %>% dplyr::filter(mpg >30 | cyl >= 4)"),
    learnr::answer("x %>% dplyr::select(cat == CityCar)"),
    learnr::answer("x %>% dplyr::filter(mpg >30, cyl >= 4)", correct = TRUE),
    allow_retry = T
  )
)
```

You want to exclude cars with cyl = 8.

```{r notequal}
learnr::quiz(
  learnr::question("Which command(s) is (are) correct?",
    learnr::answer("x %>% dplyr::filter(cyl =! 8)"),
    learnr::answer("x %>% dplyr::filter(!cyl == 8)", correct = TRUE),
    learnr::answer("x %>% dplyr::filter(cyl != 8)", correct = TRUE),
    learnr::answer("x %>% dplyr::filter(cyl <> 8)"),
    allow_retry = T
  )
)
```

## Sorting

```{r,echo = F}
x 
```

You want to find the most fuel efficient cars: 

```{r sorting}
learnr::quiz(
  learnr::question("Which command(s) is (are) correct?",
    learnr::answer("x %>% dplyr::arrange(mpg)"),
    learnr::answer("x %>% dplyr::sort(mpg)"),
    learnr::answer("x %>% dplyr::arrange(dplr::desc(mpg))", correct = TRUE),
    learnr::answer("x %>% sort(mpg)"),
    learnr::answer("x %>% sort(dlyr::desc(mpg))"),
    allow_retry = T
  )
)
```

## Long vs Wide Data frames

Using the following data frame `x`:

```{r,echo = F}
x 
```

### Long or Wide?

```{r longorwide}
learnr::quiz(
  learnr::question("Is it a long or wide data frame?",
    learnr::answer("Wide", correct = TRUE),
    learnr::answer("Long"),
    allow_retry = T
  )
)
```

### Packages and Functions

```{r ff}
learnr::quiz(
  learnr::question("Which functions would you use?",
    learnr::answer("pivot_longer() and pivot_wider()", correct = TRUE),
    learnr::answer("wide_2_long() and long_2_wide()"),
    allow_retry = T
  )
)
```

```{r rightlib}
learnr::quiz(
  learnr::question("Which package do the right functions belong to?",
    learnr::answer("tidyr", correct = TRUE),
    learnr::answer("dplyr"),
    learnr::answer("convert-df"),
    learnr::answer("ggplot"),
    allow_retry = T
  )
)
```

```{r pivot}
learnr::quiz(
  learnr::question("Which function has the names_to and values_to arguments?",
    learnr::answer("pivot_wider"),
    learnr::answer("pivot_longer", correct = TRUE),
    allow_retry = T
  )
)
```

### Grouping

You want to compute the average `mpg` by `cyl`.

```{r,echo = F}
x 
```

```{r group_by}
learnr::quiz(
  learnr::question("Select the appropriate command.",
    learnr::answer("x %>% dplyr::summarise(mean(mpg))"),
    learnr::answer("x %>% dplyr::summarise(mean(mpg)) %>% dplyr::group_by(cyl)"),
    learnr::answer("x %>% dplyr::group_by(cyl) %>% dplyr::summarise(mean(mpg))", correct = TRUE),
    allow_retry = T
  )
)
```
## Lags

We are now extracting stock prices for ExxonMobil and Citibank.

```{r}
(y <- tidyquant::tq_get(c("XOM", "C"),
              get  = "stock.prices",
              from = "2016-01-01",
              to = as.character(Sys.Date())) %>% dplyr::select(date,symbol,close) %>% dplyr::arrange(date))
```

```{r bracket}
learnr::quiz(
  learnr::question("Why did we wrap the assignment in ()?",
    learnr::answer("It looks better on the output."),
    learnr::answer("It assigns the output to a variable and prints it.", correct = T),
    learnr::answer("I copied and pasted from a website and don't understand what I did."),
    allow_retry = T
  )
)
```

You want to compute to compute the average daily change in stock price in simple percentage terms:

```{r ave}
learnr::quiz(
  learnr::question("What commands would you run?",
    learnr::answer("y %>% dplyr::group_by(symbol) %>% dplyr::mutate(return = (close / dplyr::lag(close))-1) %>% dplyr::summarise(mean(return))
"),
    learnr::answer("y %>% dplyr::group_by(symbol) %>% dplyr::mutate(return = (close / dplyr::lag(close))-1) %>% stats::na.omit()
"),
    learnr::answer("y %>% dplyr::group_by(symbol) %>% dplyr::mutate(return = (close / dplyr::lag(close))-1) %>% stats::na.omit() %>% dplyr::summarise(mean(return))

", correct = TRUE),
    allow_retry = T
  )
)
```
## xts objects

```{r xts1}
learnr::quiz(
  learnr::question("If you wanted to convert stock prices from XOM and C in xts format, what function would you use?",
    learnr::answer("Convert2xts()"),
    learnr::answer("dplyr::tk_xts "),
    learnr::answer("timetk::tk_xts", correct = TRUE),
    allow_retry = T
  )
)
```




