---
title: "DSCF Quiz 3"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(learnr)
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = FALSE,
                      fig.width = 9, fig.height = 6,fig.align = "center",
                      tidy = FALSE, strip.white = TRUE, out.width = '100%')
library(gt)
bd_txt <- function(x,title = "Grading",subtitle = "-", width = 700) {
  if (nchar(gsub(" ","",subtitle))==0) {subtitle <- "-"}
  y <- x %>% gt::gt() %>%
    gt::tab_header(title = title, subtitle = subtitle) %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(cell_fill(color = "royalblue"),
                               cell_text(color = "white",weight = "bold")),
                  locations = cells_title(groups = c("title")))
  y= y %>% tab_options(table.width = px(width),table.font.size = pct(80))
  return(y)
}

bd_lo <- function(x,width=700) {
  y <- x %>% gt::gt(rowname_col = rownames(.)) %>%
    gt::tab_header(title = "Learning Objectives",
                   subtitle = "Desired Outcomes Sought for Mastery of Material") %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(cell_fill(color = "royalblue"),
                               cell_text(color = "white",weight = "bold")),
                  locations = cells_title(groups = c("title")))
  y= y %>% tab_options(table.width = px(width),table.font.size = pct(80))
  return(y)
}


from = as.Date("2018-01-01")
to = lubridate::rollback(Sys.Date())
```

## Problem We Are Solving

**This quiz consists in performing a multivariate regression.**

This exercise is quiz #3 - see grading section.

### Variables considered:

+ NANR with the [SPDR® S&P® North American Natural Resources ETF](https://www.ssga.com/us/en/individual/etfs/funds/spdr-sp-north-american-natural-resources-etf-nanr).
+ US equities with the [SPDR S&P 500 ETF](https://etfdb.com/etf/SPY/#etf-ticker-profile).
+ Oil with the [United States Oil Fund](https://etfdb.com/etf/USO/#etf-ticker-profile).
+ Natural Gas with the [United States Natural Gas Fund](https://www.uscfinvestments.com/ung).
+ Gold with the [SPDR Gold Trust](https://etfdb.com/etf/GLD/#etf-ticker-profile).
+ Silver with the [iShares Silver Trust](https://www.ishares.com/us/products/239855/ishares-silver-trust-fund).

```{r}
tickers <-  c("NANR","SPY","USO","UNG","GLD","SLV")
```

### Your Ask

The ask consists in demonstrating your ability to explain the performance of `NANR` as a function of the other variables in a multivariate regression framework.

In a concise .Rmd (i.e. no `flexdashboards`), follow the workflow in the class note module on multivariate regressions.

1. Extract data from `r from` to `r to` and compute daily `log()` returns.You do NOT need to print data wrangling in any final document.
2. Provide a correlation matrix and/or pairs plot and comment on whether and where you see potential issues with multicollinearity.
3. Compute regressions by recursively adding independent variables.
4. Compute the Variance Inflation Factor ("VIF") for all your regressions.
5. Make a clear recommendation on which multivariate regression model you deem best and the reasons why. Use all the knowledge you gained on regressions up to this point in class.

## Grading

This is an advanced class in your degree and/or professional workplace and you are judged both on absolute and relative standards versus your peers. You are focused on building skills to support your future career success.

```{r, echo=F,include=TRUE, fig.height=3}
tibble(Competency=c("Presentation",
                    "Cor Matrix / Pairs Plot",
                    "Recursive Regressions",
                    "VIF",
                    "Recommended Regression"),
           Measure=c("Professionally rendered and document clean of unnecessary code/clutter not relevant to the story. Assume you are presenting to a business leader interested in the story, not how you got to it.",
                   "Insightful interpretation.",
                   "Models properly defined and no errors in computations.",
                   "Correct implementation.",
                   "Ability to apply concepts towards a final practical recommendation with sound logic."),
           Score=c("1.5 points",
                   "1.5 points",
                   "2 points",
                   "1 point",
                   "4 points")) %>% bd_lo()
```

## Solution Hint

**No hints provided.**

```{r, echo = F, eval=F}
library(tidyquant)
ret <- tidyquant::tq_get(tickers,
              get  = "stock.prices",
              from = from,
              to = to) %>% 
  dplyr::select(date, symbol,close = adjusted) %>% 
  dplyr::group_by(symbol) %>% 
  dplyr::mutate(ret = log(close / dplyr::lag(close)))  %>% 
  tidyr::pivot_wider(date, names_from = symbol, values_from = ret) %>% 
  stats::na.omit()
```

```{r, echo = F, eval = F}
library(gt)
ret %>% 
  dplyr::select(-date,-NANR) %>%  # exclude date and outcome, leave only predictors 
  purrr::map(~lm(NANR ~ .x, data = ret)) %>% 
  purrr::map(summary) %>% 
  purrr::map_dbl("r.squared") %>% 
  tibble::tibble(Predictors = names(.),r.squared = .) %>% 
  dplyr::arrange(desc(.[[2]])) %>% 
  gt() %>% 
  gt::fmt_percent(columns = !matches("Predictors"), decimals = 1)
```



```{r, echo = F, eval=F}
fit1 <- stats::lm(NANR ~ SPY,ret)
fit2 <- stats::lm(NANR ~ SPY + USO,ret)
fit3 <- stats::lm(NANR ~ SPY + USO + SLV,ret)
fit4 <- stats::lm(NANR ~ SPY + USO + SLV + GLD,ret)
fit5 <- stats::lm(NANR ~ SPY + USO + SLV + GLD + UNG,ret)
```

```{r, echo = F, eval=F}
ret %>% GGally::ggpairs()
```

```{r, echo = F, eval=F}
ret %>% RTL::chart_pairs()
```

```{r, echo = F, eval=F}
library(broom)
fit1 %>% broom::glance() %>% 
  dplyr::add_row(fit2 %>% broom::glance()) %>% 
  dplyr::add_row(fit3 %>% broom::glance()) %>% 
  dplyr::add_row(fit4 %>% broom::glance()) %>% 
  dplyr::add_row(fit5 %>% broom::glance()) %>% dplyr::select(1:5)
```

```{r, echo = F, eval=F}
dplyr::bind_rows(car::vif(fit2),
                 car::vif(fit3),
                 car::vif(fit4),
                 car::vif(fit5)) %>% 
  gt() %>% 
  gt::fmt_number(columns = everything(),decimals = 3) %>% 
  gt::tab_style(style = list(cell_fill(color = "lightgreen"),
                                 cell_text(weight = "bold")),
                    locations = cells_body(columns = everything(),
                                           rows = everything() <= 2
                                           )
  )
```

```{r, echo = F, eval=F}
# possible reasonable recommendations
summary(stats::lm(NANR ~ SPY + USO + GLD,ret))
summary(stats::lm(NANR ~ SPY + USO + SLV,ret))
# also possible if purely statistics but not trading
summary(stats::lm(NANR ~ SPY + USO + SLV + GLD,ret))

```

