---
title: "Assessing Fitness with Strava Data"
output: 
  html_document:
    self_contained: true
    theme:
      bg: "#2B3E50"
      fg: "#EBEBEB"
      primary: "lime"
      secondary: "#51616F"
      base_font:
        google: Prompt
      heading_font:
        google: Prompt
      code_font:
        google: JetBrains Mono
---

##  {.tabset .tabset-pills}

Read carefully what is being asked to deploy your newly acquired data science skills producing quality business documents. 

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(dplyr)
library(gt)
library(lubridate)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  fig.width = 9,
  fig.height = 6,
  fig.align = "center",
  tidy = FALSE,
  strip.white = TRUE,
  out.width = '100%'
)
bd_txt <-
  function(x,
           title = "Grading",
           subtitle = "-",
           width = 700) {
    if (nchar(gsub(" ", "", subtitle)) == 0) {
      subtitle <- "-"
    }
    y <- x %>% gt::gt() %>%
      gt::tab_header(title = title, subtitle = subtitle) %>%
      gt::tab_style(style = cell_text(weight = "bold"),
                    locations = cells_column_labels(colnames(.))) %>%
      gt::tab_style(style = list(
        cell_fill(color = "royalblue"),
        cell_text(color = "white", weight = "bold")
      ),
      locations = cells_title(groups = c("title")))
    y = y %>% tab_options(table.width = px(width),
                          table.font.size = pct(80))
    return(y)
  }

bd_lo <- function(x, width = 700) {
  y <- x %>% gt::gt(rowname_col = rownames(.)) %>%
    gt::tab_header(title = "Learning Objectives",
                   subtitle = "Desired Outcomes Sought for Mastery of Material") %>%
    gt::tab_style(style = cell_text(weight = "bold"),
                  locations = cells_column_labels(colnames(.))) %>%
    gt::tab_style(style = list(
      cell_fill(color = "royalblue"),
      cell_text(color = "white", weight = "bold")
    ),
    locations = cells_title(groups = c("title")))
  y = y %>% tab_options(table.width = px(width),
                        table.font.size = pct(80))
  return(y)
}


from = as.Date("2008-01-01")
to = lubridate::rollback(Sys.Date())
```

### Framing the Problem

+ You are a running coach specializing in what you might consider `...older...` people. You know the generation that may provide  guidance you quickly discard because `...things are different...`. 
+ Your goal here extends beyond measuring statistics and executing code.
+ You will need to provide an assessment of fitness (level and improvement) for these two individuals. The data comes from two of your Professors so be kind in your assessments!
+ Extra points if you also add yours or another individual.

```{r, echo=FALSE}
url <- "https://i2.wp.com/kevinspear.com/wp-content/uploads/2017/09/Spear-4096.jpg?resize=750%2C496"
knitr::include_graphics(url)
```

### Skills Practiced & Requirements

+ Defining a problem to solve. Here I am not giving you how we define `fitness`, much like in a real-world problem. This is your first experimentation developing a skill that is critical in the workplace. 
+ Data wrangling and parsing.
+ Data type conversion which is part of the `learn-to-learn` objectives of this class. For example, you will have to make decisions on how you express the pace of a runner, defined in minutes:seconds in the dataset. 
+ You must make use of the material covered up to and inclusive to the class prior to handling over the assignment.
+ Choice of effective visualization in communication.
+ Data analytics and an ability to tell a story from it.
+ Clean rendering of a business document. The standard for assessment will be higher than the prior assignment as you obtained feedback from it.

### Data

The data is provided in the `RTLedu::strava` dataset. You will need to update `RTLedu` on the day the assignment is given in class. 

### Your Ask

The client requested answers to the following questions:

1. Explain how you define fitness.
2. Tell me about which individual is fitter?
3. Tell me about which individual has improved more in fitness?
4. Make a clear and concise recommendation on which individual you would want to coach. There is no `it depends here`, you have to make a decision.

Write a bullet point summary on your findings at the beginning of the document.

You must use a quarto document (<FirstnameLastname>.qmd) and render it into `html`.  **I will not accept a <quiz2.qmd> document as an acceptable document. It will attract a 25% penalty before I grade it.**


### Grading

If you take this exercise as part of a graded item in a course, see the Grading section in class notes. 

