---
title: "Spot to Forward Relationship"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
fwd <- function(S0 = 1000,
                r = 0.1,
                d = 0,
                T = 1) {
  tmp <- S0 * exp((r - d) * T)
  return(tmp)
}
```

<br>
<br>

**Internalizing an Equation: Spot to Forward Equation.**

+ **The quality of learning is defined as understanding, not remembering.**
+ **Being mindful, or in the conversation, supports understanding.**
+ **Reading text(book)s primarily supports remembering.**
+ **Creating your own questions allows you to internalize learning and improve recall in other contexts.**

$$\begin{aligned}
F = S e^{(r-d)*T}\quad
\end{aligned}$$

## Directional Relationship

```{r IEq1}
learnr::quiz(
  learnr::question("Which statement(s) is (are) correct? The value of F increases when:",
    learnr::answer("S, d and T increase."),
    learnr::answer("S and T increase.",correct = T),
    learnr::answer("S, r and T increase.",correct = T),
    random_answer_order = TRUE
  )
)
```

## Type of Relationship

Thinking of the relationship between $F$ and the dependent variables:

```{r IEq2}
learnr::quiz(
  learnr::question("Which dependent variable(s) have a linear relationship to F?",
    learnr::answer("S",correct = T),
    learnr::answer("r"),
    learnr::answer("d"),
    learnr::answer("T"),
    random_answer_order = TRUE
  )
)
```

## Exploring the Relathionship

Using the functions `fwd()` and `plot()`, generate a plot showing the value of $F$, when $T$ is between 1 and 100. 

Hints:

+ Typing the function name without `()` prints the function. Try with `fwd()`.
+ `plot(fwd(...))` to visualize relationships.
+ Functions may take vectors as arguments and return vectors in the output.

```{r explore, exercise=TRUE}

```
