---
title: "Risk Management ETRM"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE, message=FALSE, warnings = F}
library(learnr)
library(dplyr)
library(tidyr)
library(lubridate)
library(RTLedu)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  fig.width = 8,
  fig.height = 6,
  fig.align = "center",
  tidy = FALSE,
  strip.white = TRUE,
  out.width = '100%'
)
```

## Framing

+ You are newly employed as a risk analyst for an energy trading firm.
+ The company is a top 100 employer and cares about employee development.
+ It has provided you with training on exposure and Profit and Loss ("PL").
+ Now it is wanting to test the effectiveness of that training. 

## Skills Practiced

+ Data wrangling and parsing.
+ Choice of effective visualization in communication.
+ Understanding exposure and PL.

## Data

The `RTLedu::deals` dataset contains trades in a commodity trading game. 

+ `user` refers to the trader.
+ `DEALPRICE` refers to the trade execution price.
+ The prices and units depend on the futures contract traded.

```{r}
RTLedu::deals
```

The `RTLedu::risk` dataset contains the output of the End Of Day ("EOD") risk process.

+ `MARKPRICE` refers to the MTM on each EOD.

```{r}
RTLedu::risk
```


## Your Ask

Using Rmarkdown, render into `html` the following information. 

1. A chart showing the cumulative PL of all traders:

<br>

```{r, echo=FALSE}
rr <- risk %>% 
  dplyr::mutate(PL = (MARKPRICE - DEALPRICE) * QUANTITY,
                asofdate = as.Date(asofdate),
                Contract = paste0(TICKER,"-",CONTRACT),
                Quantity = dplyr::case_when(UNIT == "GAL" ~ QUANTITY / 42, TRUE ~ QUANTITY),
                #ContractMonth = tsibble::yearmonth(paste0(as.character(YEAR),as.character(MONTH)),"%Y%m")) %>% 
                ContractMonth = as.Date(paste(as.character(YEAR),as.character(sprintf("%02d", as.numeric(MONTH))),"01",sep = "-"))) %>% 
                #ContractMonth = as.character(paste0(as.character(YEAR),as.character(sprintf("%02d", as.numeric(MONTH)))))) %>% 
  
  dplyr::group_by(user,asofdate,Contract,ContractMonth,TICKER) %>% 
  dplyr::summarise(Expo = sum(Quantity),
                   PL = sum(PL),
                   .groups = "keep")

allusers <- c("playercl1", "playerrbob1", "playerho1", "playerng1")

rr %>% 
  dplyr::filter(user %in% allusers) %>% 
  dplyr::group_by(user,asofdate) %>% 
  dplyr::summarise(PL = sum(PL), .groups = "drop") %>% 
  tidyr::pivot_wider(names_from = user, values_from = PL) %>% 
  dplyr::mutate(across(where(is.numeric), ~replace_na(.x, 0))) %>% 
  tidyr::pivot_longer(-asofdate, names_to = "user", values_to = "PL") %>% 
  dplyr::arrange(user, asofdate) %>% 
  plotly::plot_ly(x = ~asofdate, y = ~PL, name = ~user, type = "scatter", mode = "line") %>% 
  plotly::layout(xaxis = list(tickformat = "%Y%m", type = "category"))
```

<br>

2. A heatmap showing the priced exposure in barrels for trader `playerrbob1` for the last EOD run.
<br>
```{r, echo=FALSE}
cPalette <- colorRampPalette(c("hotpink","lawngreen"))
eod <- max(risk$asofdate)
rr %>% 
  dplyr::filter(asofdate == eod,
                user == "playerrbob1") %>% 
  plotly::plot_ly(x = ~ContractMonth, y = ~TICKER, z = ~Expo, type = "heatmap", text = ~Expo, colors = cPalette(10)) %>% 
  plotly::add_annotations(x = ~ContractMonth,
                          y = ~TICKER,
                          showarrow = FALSE,
                          align = "center") %>% 
  plotly::layout(xaxis = list(tickformat = "%Y%m", type = "category"))
```
<br>

3. Using the `deals` dataset, you are interested in assessing how often traders transact. This is an insightful data point to inform their journey towards actively managing market calls in light of changing market conditions.

<br>
```{r, echo=FALSE}
gameDates <- dplyr::tibble(date = unique(risk$asofdate))
deals %>% 
  dplyr::filter(user %in% allusers) %>% 
  dplyr::mutate(date = as.Date(EODTime, "%Y-%m-%d")) %>% 
  dplyr::group_by(user,date) %>% 
  dplyr::count() %>% 
  dplyr::rename(trades = n) %>% 
  dplyr::arrange(date) %>% 
  plotly::plot_ly(x = ~date, y = ~trades, name = ~user, type = "bar") %>% 
  plotly::layout(yaxis = list(tickvals = ~trades),
                 xaxis = list(title = "", tickvals = gameDates))
```


